`r params$set_title`

### 2017-10-12 lib/Report.Rmd
organizing

```{r setup, echo = FALSE}
opts_chunk$set(echo = FALSE)
city <- params$city
state <- params$state
read_chunk('test.R')
```

```{r part1}
```

Hi Dan,

>>>>

```{r setup, echo = FALSE}
opts_chunk$set(echo = FALSE)
city <- params$city
state <- params$state
read_chunk('test.R')
```
# https://stackoverflow.com/questions/14796501/is-it-possible-to-call-external-r-script-from-r-markdown-rmd-in-rstudio
# https://stackoverflow.com/questions/23597140/how-to-find-the-percentage-of-nas-in-a-data-frame-using-apply

```{r part1}
annotate with ## @knitr part1 in script
x %>% summarize_all(funs(sum(is.na(.)) / length(.)))
```
